---
title: "Untitled"
author: "Pradeepti"
date: "5/28/2020"
output: html_document
---
```{r}
require(tidyverse)

```

```{r}
df=read_csv('R:\\LEARN\\Data analyst training\\Cars.csv')
```

```{r}
str(df)
```

```{r}
summary(df)
```

plotting to find multicollinearity of the i/p variables. So, VOL-WT, HP-SP have multicollinearity.
```{r}
#plot(df)
pairs(df)
```

```{r}
cor(df$HP, df$MPG)
cor(df$HP, df$VOL)
cor(df$HP, df$SP)
cor(df$HP, df$WT)

```

Building a basic model. p value for vol and wt is higher than 0.05. so they are not significant.
```{r}
m1=lm(MPG~HP+VOL+SP+WT, data = df)
summary(m1)
```

building seperate models for vol and wt, they are significant
```{r}
mv = lm(MPG~VOL, data = df)
summary(mv)
```

```{r}
mw=lm(MPG~WT, data = df)
summary(mw)
```

building a model combining vol+wt, both became insignificant. So independently they are ok, combined, they become insignificant.
```{r}
mvw = lm(MPG ~ VOL + WT, data = df)
summary(mvw)
```

installed car and mvinfluence packages
```{r}
require(car)
require(mvinfluence)
```

plotting influence plot to identify the problematic records. StudRes> +or-2 and Cooks distance>0.5 for rows 1, 71, 77
```{r}
influencePlot(m1)
```

building model after removing the 3 records, still not significant
```{r}
nm = lm(MPG ~ HP + VOL + SP + WT, data = df[-c(1,71,77),])
summary(nm)
```

trying VIF, wt has highest value. so building a model without wt
```{r}
vif(nm)
```

model without wt
```{r}
fm = lm(MPG ~ HP + VOL + SP, data = df)
summary(fm)
```

trying AV Plot 
```{r}
avPlots(m1)
avPlots(fm)
```
vif for final model
```{r}
vif(fm)
```

predicting values
```{r}
pv = predict(fm, data = df)
pv = as.data.frame(pv)
pv
```

```{r}
data = data.frame(pv, df)
data
```

