---
title: "Untitled"
author: "Pradeepti"
date: "6/2/2020"
output: html_document
---
```{r}
require(tidyverse)
```

loading the dataset
```{r}
df = read_csv("claimants.csv")
```

```{r}
str(df)
```

summary. there are NA values in some columns. doing na.omit removes the missing values. but when we build the model, it automatically removes NAs. 
```{r}
summary(df)
```

```{r}
new = na.omit(df)
summary(new)
```

building the logistic regression model. converting the categorical data as factors. 
seatbelt and age are not significant acc. to this model.
also, null deviance > residual, so i/p variables are relavent to o/p variable.
```{r}
m1 = glm (ATTORNEY ~ factor(CLMSEX) + factor(CLMINSUR) + factor(SEATBELT) + CLMAGE + LOSS, family = binomial, data = df)
summary(m1)
```


```{r}
coef(m1)
```

o/p is now in log values, so taking exp to get original values. 
```{r}
exp(coef(m1))
```
predicting
```{r}
prob = predict(m1, data = df)
pvprob = as.data.frame(prob)
pvprob
```

the original df has null values but the pv values excluded them. so do cbind to the new df which had the null values removed. 
```{r}
cbind(pvprob, new)
```

```{r}
table(new$ATTORNEY)
table(df$ATTORNEY)
```
building confusion matrix for actual and predicted values. TRUES = 485 + 93 = 578, FALSE = 260 + 258 = 518
```{r}
table(prob >=0.5)
conf = table(new$ATTORNEY, prob >=0.5)
conf
```

calculating the accuracy, 67%
```{r}
acc = sum(diag(conf))/sum(conf)
acc
```
