---
title: "Hierarchical Clustering"
author: "Pradeepti"
date: "7/1/2020"
output: html_document
---
```{r}
require(tidyverse)
```

```{r}
df = read_csv("R:\\LEARN\\Data analyst training\\Universities.csv")
```

data columns have scaling issues.
```{r}
#str(df)
summary(df)
```

normalizing the data. excluding 1st column as it is not numeric
```{r}
norm_df = scale(df[,2:7])
norm_df
```

calculating the euclidean distance
```{r}
d = dist(norm_df, method = 'euclidean')
d
```

building the hierarchical cluster model
```{r}
m1 = hclust(d, method = 'complete')
plot(m1, hang = -1)
```

cutting the clusters with cluster numbers for all records
```{r}
clusters = cutree(m1, k = 5)
clusters = as.data.frame(clusters)
```

adding borders to dendrogram
```{r}
plot(m1, hang = -1)
rect.hclust(m1, k = 5, border = 'purple')
```

combining cluster number to original dataframe
```{r}
final_df = cbind(clusters, df)
final_df
```

finding the means to know the avg values of each column.
```{r}
aggregate(final_df[,3:8], by = list(final_df$clusters), FUN = mean)
#final_df %>% group_by(final_df$clusters) %>% summarise(final_df[,3:8] = mean(final_df[3:8]))
```

```{r}

```

```{r}

```

```{r}

```

