---
title: "PCA"
author: "Pradeepti"
date: "7/10/2020"
output: html_document
---

```{r}
require(tidyverse)
```

universities dataset to predict grad rate
```{r}
df = read_csv("R:\\LEARN\\Data analyst training\\Universities.csv")
str(df)
```

creating a new df excluding the 1st column as it is non numeric
```{r}
ndf = df[-1]
ndf
```

finding correlation. there is high multi collinearity amongst the variables. 
```{r}
attach(ndf)
cor(ndf)
```

normalising the data to get rid of scaling issues
```{r}
normdf = scale(ndf)
normdf
```

performing PCA. o/p has SD and variation in descending order
```{r}
pcaobj = princomp(normdf)
summary(pcaobj)
```

Then do loadings to see weights(a’s). The blank values are very small values that are not displayed but are calculated internally. Then do a plot of the values
```{r}
loadings(pcaobj)
plot(pcaobj)
```
to get 95% of the data we need to include the 1st 3 columns. doing a cbind of original df and the scores
```{r}
newdf = cbind(df, pcaobj$scores[,1:3])
newdf
```

creating a new df for grad rate and PCs.
```{r}
fdf = newdf[,7:10]
fdf
```

building a linear regression model to predict the grad rate using PCs, variables are significant and accuracy is 94%
```{r}
m1 = lm(GradRate ~ Comp.1 + Comp.2 + Comp.3, data = fdf)
summary(m1)
```

building a model with original values just to compare how accurate using PCA was. variables are insignificant, have multicollinearity, accuracy is also not good. 
```{r}
m2 = lm(GradRate ~ SAT + Top10 + Accept + SFRatio + Expenses, data = ndf)
summary(m2)
```

```{r}
attach(fdf)
cor(fdf)
```

```{r}

```

```{r}

```

