---
title: "DECISION TREES"
author: "Pradeepti"
date: "7/10/2020"
output: html_document
---
installing packages tree and C50 for decision trees. caret package is to split data into test and training set
```{r}
install.packages("tree")
install.packages("C50")
install.packages("caret")
require(C50)
require(caret)
```

data() shows all available datsets. choosing iris dataset to work on
```{r}
#data()
iris
```

using caret package to split data to test(30%) and train set(70%)
```{r}
intrain = createDataPartition(y = iris$Species, p = 0.70, list = FALSE)
traindf = iris[intrain,]
testdf = iris[-intrain,]
```

building a model in train data. format is C5.0(x,y)
```{r}
#m1 = C5.0(traindf[,-5], traindf[,5]) 
m1 = C5.0(traindf[,-5], traindf$Species)
plot(m1)
```

checking train df accuracy. 98%
```{r}
table(traindf$Species)
table(predict(m1, traindf))
mean(traindf$Species == predict(m1, traindf))
```

building model for test set
```{r}
m2 = C5.0(testdf[,-5], testdf$Species)
plot(m2)
```

checking test set accuracy
```{r}
mean(testdf$Species == predict(m2, testdf))
```

comparing actual and predicted values with cross table. gmodels package is needed
```{r}
install.packages("gmodels")
require(gmodels)
```

```{r}
#summary(iris)
CrossTable(testdf$Species, predict(m2, testdf))
```

