---
title: "KNN"
author: "Pradeepti"
date: "7/13/2020"
output: html_document
---
```{r}
require(tidyverse)
require(readr)
```

case study: predicting cancer(M:Malignant/ B:Benign) based on other input variables using KNN
```{r}
df = read_csv("R:\\LEARN\\Data analyst training\\cancer.csv")
```


```{r}
summary(df)
```

removing the first column as it is not needed in analysis
```{r}
df = df[-1]
head(df)
table(df$diagnosis)
```

variable diagnosis should be a factor, not character, so changing it
```{r}
df$diagnosis =factor(df$diagnosis, levels = c("B", "M"), labels = c("Benign", "Malignant"))
str(df)
```

finding the proportion of M, B and rouding off to 3 decimal points. 357/569, 212/569
```{r}
round(prop.table(table(df$diagnosis))*100, digits = 2)
```

checking summary statistics to identify scaling issues
```{r}
summary(df[c("radius_mean", "area_mean", "smoothness_mean")])
#summary(df[, c(2,5,6)])
```

normalizing to resolve scaling issues(exclusing 1st column)and converting to a df data structure
```{r}
ndf = as.data.frame(scale(df[,2:31]))
class(ndf)
```

summary statistics of normalized data
```{r}
summary(ndf[,c(1,4,5)])
```

splitting the dataset to train and test for i/p variables. normalized df doesnt have the o/p variable diagnosis
```{r}
xtrain = ndf[1:469,]
xtest = ndf[470:569,]
dim(xtrain)
dim(xtest)
```

train and test sets for o/p variable. we take this from original df as only that has the y variable. 
```{r}
ytrain = df[1:469, 1]
ytrain = as.data.frame(ytrain)
ytrain = as.factor(ytrain[[1]])
ytest = df[470:569, 1]
ytest = as.data.frame(ytest)
ytest = as.factor(ytest[[1]])
str(ytrain)  

```

installing class package to implement knn. xtrain will be used to build the model, xtest to test it and ytrain is the respective o/p of the model.
```{r}
#library(class)
m1 = knn(xtrain, xtest, ytrain, k=3)
m1
```

ytest will be actual values and model o/p will be predicted values. so for accuracy we can compare both
```{r}
mean(ytest == m1)
```

another way to get accuracy - confusion matrix with gmodels library. 59+37 = 96/100. same accuracy 96%
```{r}
library(gmodels)
table(ytest)
CrossTable(ytest, m1)
```


```{r}

```

